Mixing time estimation in reversible Markov chains from a single sample path

### 2015-06-02 intro-nips.tex
main results road map

  \item
    In \cref{sec:rates-lower}, we show in
    \cref{thm:lb-pimin,thm:lb-gap} that $n = \Omega\parens{ (d\log
    d)/\gap + 1/\pimin}$ observations are necessary for any procedure
    to guarantee constant multiplicative accuracy in estimating $\gap$
    (\cref{thm:lb-pimin,thm:lb-gap}).
    Essentially, \emph{every} state may need to be visited about
    $\log(d)/\gap$ times, on average, before an accurate estimate of
    the mixing time can be provided, regardless of the estimation
    procedure used.

>>>>

  \item
    In \cref{sec:rates-lower}, we show that $n = \Omega\parens{ (d\log
    d)/\gap + 1/\pimin}$ observations are necessary for any procedure
    to guarantee constant multiplicative accuracy in estimating $\gap$
    (\cref{thm:lb-pimin,thm:lb-gap}).
    Essentially, \emph{every} state may need to be visited about
    $\log(d)/\gap$ times, on average, before an accurate estimate of
    the mixing time can be provided, regardless of the estimation
    procedure used.
